Automated Topic Naming

### 2012-01-20 ese/ese-major-response.tex
minor edits

Within this new revisions, we addressed this issue in the inter-rater
reliability section and referenced this discussion in the threats to
validity and the conclusion.

>>>>

Within this new revision, we addressed this issue in the inter-rater
reliability section and referenced this discussion in the threats to
validity and the conclusion.
